---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# visian

<!-- badges: start -->
<!-- badges: end -->

Visian is a package which helps you determine the number of non-zero values in your dataset.

## Installation

You can install the development version of visian from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/visian", build_vignettes = TRUE)

```

## Example

This is a basic example which shows you how to count the number of non-zero elements of simple numeric vectors.

```{r}
library(visian)
num_vec <- c(1,2,3,4,5,0,0,0)
countNonZero(num_vec)
```

However, the function can also be used with non-standard inputs, including character and boolean vectors, as well as dataframes. It does not calculate on data which has NAs present.

```{r}
str_vec <- c("A", "B", "0")
countNonZero(str_vec)

bool_vec <- c(FALSE, TRUE, TRUE, FALSE)
countNonZero(bool_vec)
```



I hope you find this package useful and robust.
