---
title: "Count Non Zeros"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Count Non Zeros}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(visian)

```

Data often requires some pre-processing to ensure the validity of data. The visian package provides this functionality. Currently, it features just one function - `countNonZero()` - allowing a clean base-R function to interpret data and models.

### Counting zeros in numeric data
This function is very flexible and works on a variety of inputs. In its simplest usage, this function takes in an ordinary numeric vector, and returns the number of non-zero elements. 

```{r numer}
countNonZero(seq(0,5))
```

### Counting zeros in non-numeric data
However, the function handles non-typical inputs as well, such as string vectors and boolean vectors:

```{r}
string_vec <- countNonZero(c("0", "0", "1", "2"))
bool_vec <- countNonZero(c(FALSE, TRUE, TRUE, TRUE, FALSE))
print(paste("String Vector =",string_vec))
print(paste("Boolean Vector =",bool_vec))
```

### Counting zeros on columns of a dataframe
In more practical usage, you may decide to run the function on a specific column of the dataframe. In this example, we'd be interested in counting the number of people who have first aid training.

```{r}
df <- data.frame('Name'=c("John", "Sarah", "Jeff", "Karen", "James"), "First_Aid_Training"=c(0,1,1,0,1))
countNonZero(df$First_Aid_Training)
```

### Counting zeros on an entire dataframe
And you might be interested in getting a grand summary of a dataframe, on every column of the data-frame, in which the integers report the number of non-zero values in each column.

```{r}
df_nums <- data.frame('Name'=c("John", "Sarah", "Jeff", "Karen", "James"), "First_Aid_Training"=c(0,1,1,0,1))
countNonZero(df_nums)
```

I hope this package is helpful to you!
